Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-04-20 ProbabilisticCoherence.tex
cleanup

Definition~\ref{def:reconpoint}, defines an entire family of forecast reconciliation methods including many methods currently extant in the literature. To provide a geometric interpretation, we introduce an $n \times (n-m)$ matrix $\bm{R}$ whose columns span the null space $\mathfrak{s}_{\perp}$.  For example, a straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$, is the vector $(1,-1,-1)$ which is orthogonal (in the Euclidean sense) to the columns of $\bm{S}$.  In this case, the matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$. In general, the columns of any given $\bm{R}$ matrix can also be thought of as `directions' along which incoherent point forecasts are projected onto the coherent space, and these directions need not be orthogonal to $\mathfrak{s}$. 
%$$ 
%\bm{S} = 
%\begin{pmatrix} 
%1& 1 \\ 1 & 0 \\ 0&1 
%\end{pmatrix} 
%\quad \text{and} \quad 
%\bm{R} = 
%\begin{pmatrix}  
%1 \\ -1 \\ -1 
%\end{pmatrix}.
%$$ 
%
%Further let $\{\bm{s}_1,\dots,\bm{s}_m\}$ and $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively. Then $\bm{B}=\{\bm{s}_1,\dots,\bm{s}_m, \bm{r}_1,\dots,\bm{r}_{n-m}\}$ is a basis for $\mathbb{R}^n$. Now, using the insights of Definition~\ref{def:reconpoint}, we can use the following steps to reconcile the point forecasts.

@@

@@

This definition extends the notion of forecast reconciliation to the probabilistic setting.   Under point reconciliation methods, the reconciled point forecast is equal to the unreconciled point forecast after the latter is passed through two linear mappings. Similarly, probabilistic forecast reconciliation assigns the same probability to two sets where the points in one set are obtained by passing all points in the other set through two linear mappings.  This is depicted schematically in Figure~\ref{fig:pfr_sch}.

\begin{figure}
	\input{Figs/probforerec_schematic.tex}
	\caption{Summary of probabilistic forecast reconciliation.  The probability that ${\bm y}_{t+h}$ lies in the red line segment under the reconciled probabilistic forecast is defined to be equal to the probability that ${\bm y}_{t+h}$ lies in the shaded blue area under the unreconciled probabilistic forecast.  Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic}\label{fig:pfr_sch} 
\end{figure}

>>>>

Definition~\ref{def:reconpoint}, defines an entire family of forecast reconciliation methods including many methods currently extant in the literature. To provide a geometric interpretation, we introduce an $n \times (n-m)$ matrix $\bm{R}$ whose columns span the null space $\mathfrak{s}_{\perp}$.  For example, a straightforward choice of $\bm{R}$ for the most simple three variable hierarchy where $y_{1,t}=y_{2,t}+y_{3,t}$, is the vector $(1,-1,-1)$ which is orthogonal (in the Euclidean sense) to the columns of $\bm{S}$.  In this case, the matrix $\bm{R}$ can be interpreted as a `restrictions' matrix since it has the property that $\bm{R}'\bm{y}=\bm{0}$ for coherent $\bm{y}$. In general, the columns of any given $\bm{R}$ matrix can also be thought of as `directions' along which incoherent point forecasts are projected onto the coherent space, and these directions need not be orthogonal to $\mathfrak{s}$.  A schematic of this geometric interpretation is provided in Figure~\ref{fig:pointfr_sch}. 
%$$ 
%\bm{S} = 
%\begin{pmatrix} 
%1& 1 \\ 1 & 0 \\ 0&1 
%\end{pmatrix} 
%\quad \text{and} \quad 
%\bm{R} = 
%\begin{pmatrix}  
%1 \\ -1 \\ -1 
%\end{pmatrix}.
%$$ 
%
%Further let $\{\bm{s}_1,\dots,\bm{s}_m\}$ and $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively. Then $\bm{B}=\{\bm{s}_1,\dots,\bm{s}_m, \bm{r}_1,\dots,\bm{r}_{n-m}\}$ is a basis for $\mathbb{R}^n$. Now, using the insights of Definition~\ref{def:reconpoint}, we can use the following steps to reconcile the point forecasts.

@@

\begin{figure}
	\input{Figs/pointforerec_schematic.tex}
	\caption{Summary of probabilistic point reconciliation.  The mapping $G(.)$ projects the unreconciled forecast $\hat{\bm y}$ onto   Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic}\label{fig:pointfr_sch} 
\end{figure}

@@

This definition extends the notion of forecast reconciliation to the probabilistic setting.   Under point reconciliation methods, the reconciled point forecast is equal to the unreconciled point forecast after the latter is passed through two linear mappings. Similarly, probabilistic forecast reconciliation assigns the same probability to two sets where the points in one set are obtained by passing all points in the other set through two linear mappings.  This is depicted schematically in Figure~\ref{fig:probfr_sch}.

\begin{figure}
	\input{Figs/probforerec_schematic.tex}
	\caption{Summary of probabilistic forecast reconciliation.  The probability that ${\bm y}_{t+h}$ lies in the red line segment under the reconciled probabilistic forecast is defined to be equal to the probability that ${\bm y}_{t+h}$ lies in the shaded blue area under the unreconciled probabilistic forecast.  Note that since the smallest hierarchy involves three dimensions, this figure is only a schematic}\label{fig:probfr_sch} 
\end{figure}
